---
title: "Data Cleaning"
author: "Nam Tran"
date: "3/28/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr); library(tidyverse); library(dplyr); library(psych); library(PerformanceAnalytics); library(skimr); library(lessR); library(ggplot2); library(gridExtra); library(fastDummies); library(forecast); library(BMA); library(stats); library(olsrr); library(MASS); library(kableExtra); library(car); library(broom); library(glmulti); library(ggmap); library(rstudioapi); library(revgeo); library(RCurl);library(stringr); library(gsubfn);library(ngram);library(stringr); library(tm)
```

```{r}
Listing_df_1 <- read.csv("Airbnb_DataCleaning2.csv.csv")
select_var <- c()
```
```{r}
dim(Listing_df_1)
```

#### 01. id - Remove / No need to use
#### 02. name - Keeped 
```{r}
# Use text mining to access
select_var <- c(select_var, "name")
```
#### 03. description
```{r}
# Use text mining to access
select_var <- c(select_var, "description")
```

#### 04. neighborhood_overview
```{r}
# Use text mining to access
select_var <- c(select_var, "neighborhood_overview")
```

#### 05. host_id
```{r}
# Use text mining to access
select_var <- c(select_var, "host_id")
```

#### 06. host_since / No Neet to use

#### 07. host_response_time
```{r}
# sum(is.na(Listing_df_1$host_response_time))  ---------- No missing value
select_var <- c(select_var, "host_response_time")
```

#### 08. host_response_rate
```{r}
# sum(is.na(Listing_df_1$host_response_rate)) --------- 10853 missing value / Replaced missing value by the average response rate of each host
AVG_Host_Response_Rate <- as.data.frame(pivot(Listing_df_1, compute = mean, variable = host_response_rate, by = host_id))
Listing_df_1 <- merge(Listing_df_1, AVG_Host_Response_Rate[,c(1,4)], by = "host_id")
```
```{r}
Listing_df_1[is.na(Listing_df_1$host_response_rate),"host_response_rate"] = Listing_df_1[is.na(Listing_df_1$host_response_rate),"host_response_rate_mean"] 
select_var <- c(select_var, "host_response_rate")
```

#### 09. host_acceptance_rate
```{r}
# sum(is.na(Listing_df_1$host_acceptance_rate)) --------- 10319 missing value / Replaced missing value by the average response rate of each host
AVG_Host_Acceptance_Rate <- as.data.frame(pivot(Listing_df_1, compute = mean, variable = host_acceptance_rate, by = host_id))
Listing_df_1 <- merge(Listing_df_1, AVG_Host_Acceptance_Rate[,c(1,4)], by = "host_id")
```
```{r}
Listing_df_1[is.na(Listing_df_1$host_acceptance_rate),"host_acceptance_rate"] = Listing_df_1[is.na(Listing_df_1$host_acceptance_rate),"host_acceptance_rate_mean"] 
select_var <- c(select_var, "host_acceptance_rate")
```

#### 10. host_is_superhost
```{r}
# sum(is.na(Listing_df_1$host_is_superhost))  ----- ---- No missing value
select_var <- c(select_var, "host_is_superhost")
```

#### 11. host_total_listings_count
```{r}
# sum(is.na(Listing_df_1$host_total_listings_count))  ---------- 7 missing value
Total_Listing <- as.data.frame(table(Listing_df_1$host_id))
colnames(Total_Listing) <- c("host_id","Total_listing")
Listing_df_1 <- merge(Listing_df_1, Total_Listing, by = "host_id")
Listing_df_1$host_total_listings_count <- Listing_df_1$Total_listing
sum(is.na(Listing_df_1$host_total_listings_count))
```
```{r}
select_var <- c(select_var, "host_total_listings_count")
```

#### 12. host_has_profile_pic
```{r}
# sum(is.na(Listing_df_1$host_has_profile_pic)) ---------- No missing value
select_var <- c(select_var, "host_has_profile_pic")
```

#### 13. host_identity_verified 
```{r}
sum(is.na(Listing_df_1$host_identity_verified)) #---------- No missing value
select_var <- c(select_var, "host_identity_verified")
```

#### 14. neighbourhood / No need to use

#### 15. neighbourhood_cleansed
```{r}
select_var <- c(select_var, "neighbourhood_cleansed")
```

#### 16. neighbourhood_group_cleansed
```{r}
sum(is.na(Listing_df_1$neighbourhood_group_cleansed))
select_var <- c(select_var, "neighbourhood_group_cleansed")
```

#### 17. latitude / No need to use
#### 18. longitude / No need to use
#### 19. property_type / No need to use

#### 20. room_type
```{r}
sum(is.na(Listing_df_1$room_type))   # ------- No missing value
select_var <- c(select_var, "room_type")
```

#### 21. accommodates
```{r}
sum(is.na(Listing_df_1$accommodates))   # ------- No missing value
select_var <- c(select_var, "accommodates")
```

#### 22. bathrooms_text
```{r}
sum(is.na(Listing_df_1$bathrooms_text)) # ------- No missing value
select_var <- c(select_var, "bathrooms_text")
```

#### 23. bedrooms
```{r}
sum(is.na(Listing_df_1$bathrooms_text))     # ------- No missing value
select_var <- c(select_var, "bedrooms")
```

#### 24. beds
```{r}
sum(is.na(Listing_df_1$beds))      # ------- No missing value
select_var <- c(select_var, "beds")
```

#### 25. price
```{r}
sum(is.na(Listing_df_1$price))      # ------- No missing value
select_var <- c(select_var, "price")
```

#### 26. number_of_reviews
```{r}
sum(is.na(Listing_df_1$number_of_reviews))      # ------- No missing value
select_var <- c(select_var, "number_of_reviews")
```

#### 27. number_of_reviews_ltm
```{r}
sum(is.na(Listing_df_1$number_of_reviews_ltm))      # ------- No missing value
select_var <- c(select_var, "number_of_reviews_ltm")
```

#### 28. number_of_reviews_l30d / No need to use
#### 39. first_review / No need to use
#### 30. last_review / No need to use

#### 31. review_scores_rating
```{r}
sum(is.na(Listing_df_1$review_scores_rating))  # ------- 8007 missing value    
Listing_df_1$review_scores_rating[is.na(Listing_df_1$review_scores_rating)] = 0
select_var <- c(select_var, "review_scores_rating")
```

#### 32. review_scores_accuracy
```{r}
sum(is.na(Listing_df_1$review_scores_accuracy))      # ------- 8335 missing value 
Listing_df_1$review_scores_accuracy[is.na(Listing_df_1$review_scores_accuracy)] = 0
select_var <- c(select_var, "review_scores_accuracy")
```

#### 33. review_scores_cleanliness
```{r}
sum(is.na(Listing_df_1$review_scores_cleanliness))      # ------- 8334 missing value 
Listing_df_1$review_scores_cleanliness[is.na(Listing_df_1$review_scores_cleanliness)] = 0
select_var <- c(select_var, "review_scores_cleanliness")
```

#### 34. review_scores_checkin
```{r}
sum(is.na(Listing_df_1$review_scores_checkin))      # ------- 8343 missing value 
Listing_df_1$review_scores_checkin[is.na(Listing_df_1$review_scores_checkin)] = 0
select_var <- c(select_var, "review_scores_checkin")
```

#### 35. review_scores_communication
```{r}
sum(is.na(Listing_df_1$review_scores_communication))      # ------- 8335 missing value 
Listing_df_1$review_scores_communication[is.na(Listing_df_1$review_scores_communication)] = 0
select_var <- c(select_var, "review_scores_communication")
```

#### 36. review_scores_location
```{r}
sum(is.na(Listing_df_1$review_scores_location))      # ------- 8346 missing value 
Listing_df_1$review_scores_location[is.na(Listing_df_1$review_scores_location)] = 0
select_var <- c(select_var, "review_scores_location")
```

#### 37. review_scores_value
```{r}
sum(is.na(Listing_df_1$review_scores_value))      # ------- 8348 missing value 
Listing_df_1$review_scores_value[is.na(Listing_df_1$review_scores_value)] = 0
select_var <- c(select_var, "review_scores_value")  
```

#### 38. instant_bookable
```{r}
sum(is.na(Listing_df_1$instant_bookable))      # ------- no missing value 
select_var <- c(select_var, "instant_bookable") 
```

#### 39. calculated_host_listings_count   / No need to use
#### 40. calculated_host_listings_count_entire_homes   / No need to use
#### 41. calculated_host_listings_count_private_rooms  / No need to use
#### 42. calculated_host_listings_count_shared_rooms  / No need to use

#### 43. reviews_per_month
```{r}
sum(is.na(Listing_df_1$reviews_per_month)) # ------- 8007 missing value 
Listing_df_1$reviews_per_month[is.na(Listing_df_1$reviews_per_month)] = 0
select_var <- c(select_var, "reviews_per_month")
```

#### 44. City
```{r}
sum(is.na(Listing_df_1$reviews_per_month))      # ------- no missing value 
select_var <- c(select_var, "City")
```

#### 45. State
```{r}
Listing_df_1 <- Listing_df_1[Listing_df_1$State == "CA",]
Listing_df_1 <- Listing_df_1[!is.na(Listing_df_1$State),]
dim(Listing_df_1)
select_var <- c(select_var, "State")
```

#### 46. Zip 
```{r}
sum(is.na(Listing_df_1$reviews_per_month))
select_var <- c(select_var, "Zip")
```

### 47. amenities
#### 47 amenities_count
```{r}
## creat the amenities_count from the variable amenities
corpus <- (VectorSource(Listing_df_1$amenities))
corpus <- Corpus(corpus)
## summary(corpus)
vectored <-c()

for (i in c(1:length(Listing_df_1$amenities))){
  if (length(unlist(strsplit(corpus[[i]]$content, "[,]"))) == 0){
    vectored <- c(vectored,0) }
  else if (length(unlist(strsplit(corpus[[i]]$content, "[,]"))) == 1){
    vectored <- c(vectored,0)}
  else{
    vectored <- c(vectored,length(unlist(strsplit(corpus[[i]]$content, "[,]"))))
  }
}

Listing_df_1$amenities_count <- vectored
```
```{r}
select_var <- c(select_var, "amenities_count")
```

#### 48. # 24-hour-check-in
```{r}
Listing_df_1$CheckIn24 <- ifelse(str_detect((Listing_df_1$amenities),"24-hour check-in")==TRUE,1,0)
table(Listing_df_1$CheckIn24)
```

#### 49. Air conditioning
```{r}
Listing_df_1$air_conditioning<- ifelse(str_detect((Listing_df_1$amenities),"Air conditioning|Central air conditioning")==TRUE,1,0)
table(Listing_df_1$air_conditioning)
select_var <- c(select_var, "air_conditioning")
```

#### 50. high_end_electronics
```{r}
Listing_df_1$high_end_electronics <- ifelse(str_detect((Listing_df_1$amenities),"Amazon Echo|Apple TV|Game console|Netflix|Projector and screen|Smart TV")==TRUE,1,0)
table(Listing_df_1$high_end_electronics)
```
```{r}
select_var <- c(select_var, "high_end_electronics")
```

#### 51.BBQ
```{r}
Listing_df_1$bbq <- ifelse(str_detect((Listing_df_1$amenities),"BBQ grill|Fire pit|Propane barbeque")==TRUE,1,0)
table(Listing_df_1$bbq)
select_var <- c(select_var, "bbq")
```

#### 52. balcony
```{r}
Listing_df_1$balcony <- ifelse(str_detect((Listing_df_1$amenities),"Balcony|Patio")==TRUE,1,0)
table(Listing_df_1$balcony)
select_var <- c(select_var, "balcony")
```

#### 53. nature_and_views
```{r}
Listing_df_1$nature_and_views <- ifelse(str_detect((Listing_df_1$amenities),"Beach view|Beachfront|Lake access|Mountain view|Waterfront")==TRUE,1,0)
table(Listing_df_1$nature_and_views)
select_var <- c(select_var, "balcony")
```

#### 54. breakfast
```{r}
Listing_df_1$breakfast <- ifelse(str_detect((Listing_df_1$amenities),"Breakfast")==TRUE,1,0)
table(Listing_df_1$nature_and_views)
select_var <- c(select_var, "breakfast")
```

#### 55. TV
```{r}
Listing_df_1$tv <- ifelse(str_detect((Listing_df_1$amenities),"TV")==TRUE,1,0)
table(Listing_df_1$nature_and_views)
select_var <- c(select_var, "tv")
```

#### 56. coffee_machine
```{r}
Listing_df_1$coffee_machine <- ifelse(str_detect((Listing_df_1$amenities),"Coffee maker|Espresso machine")==TRUE,1,0)
table(Listing_df_1$coffee_machine)
select_var <- c(select_var, "coffee_machine")
```

#### 57. kitchen
```{r}
Listing_df_1$kitchen <- ifelse(str_detect((Listing_df_1$amenities),"Cooking basics|kitchen|dishes|cooking")==TRUE,1,0)
table(Listing_df_1$kitchen)
select_var <- c(select_var, "kitchen")
```


#### 58. white_goods
```{r}
Listing_df_1$white_goods <- ifelse(str_detect((Listing_df_1$amenities),"Dishwasher|Dryer|Washer")==TRUE,1,0)
table(Listing_df_1$white_goods)
select_var <- c(select_var, "white_goods")
```

#### 59.elevator / No need to use
```{r}
Listing_df_1$elevator <- ifelse(str_detect((Listing_df_1$amenities),"Elevator")==TRUE,1,0)
table(Listing_df_1$elevator)

```

#### 60 gym
```{r}
Listing_df_1$gym <- ifelse(str_detect((Listing_df_1$amenities),"Exercise equipment|Gym|gym")==TRUE,1,0)
table(Listing_df_1$gym)
select_var <- c(select_var, "gym")
```

#### 61 child_friendly / No need to use
```{r}
Listing_df_1$child_friendly <- ifelse(str_detect((Listing_df_1$amenities),"Family/kid friendly|Children|children")==TRUE,1,0)
table(Listing_df_1$child_friendly)

```

#### 62 parking
```{r}
Listing_df_1$parking <- ifelse(str_detect((Listing_df_1$amenities),"parking")==TRUE,1,0)
table(Listing_df_1$parking)
select_var <- c(select_var, "parking")
```

#### 63 outdoor_space
```{r}
Listing_df_1$outdoor_space <- ifelse(str_detect((Listing_df_1$amenities),"Garden|Outdoor|Sun loungers|Terrace")==TRUE,1,0)
table(Listing_df_1$outdoor_space)
select_var <- c(select_var, "outdoor_space")
```

#### 64 host_greeting  / No need to use
```{r}
Listing_df_1$host_greeting <- ifelse(str_detect((Listing_df_1$amenities),"Host greets you")==TRUE,1,0)
table(Listing_df_1$host_greeting)
```

#### 65 hottub_sauna_pool
```{r}
Listing_df_1$hottub_sauna_pool <- ifelse(str_detect((Listing_df_1$amenities),"Hot tub|Jetted tub|hot tub|Sauna|Pool|pool")==TRUE,1,0)
table(Listing_df_1$hottub_sauna_pool)
select_var <- c(select_var, "hottub_sauna_pool")
```

#### 66 internet
```{r}
Listing_df_1$internet <- ifelse(str_detect((Listing_df_1$amenities),"Internet|Pocket wifi|Wifi|Wireless")==TRUE,1,0)
table(Listing_df_1$internet)
select_var <- c(select_var, "internet")
```

#### 67 long_term_Stay_allowed
```{r}
Listing_df_1$long_term_Stay_allowed <- ifelse(str_detect((Listing_df_1$amenities),"Long term stays allowed")==TRUE,1,0)
table(Listing_df_1$long_term_Stay_allowed)
select_var <- c(select_var, "long_term_Stay_allowed")
```

#### 68 pets_allowed / No need to use
```{r}
Listing_df_1$pets_allowed <- ifelse(str_detect((Listing_df_1$amenities),"Pets|pet|Cat(s)|Dog(s)")==TRUE,1,0)
table(Listing_df_1$pets_allowed)
```

#### 69 private_entrance
```{r}
Listing_df_1$private_entrance <- ifelse(str_detect((Listing_df_1$amenities),"Private entrance")==TRUE,1,0)
table(Listing_df_1$private_entrance)
select_var <- c(select_var, "private_entrance")
```

#### 70 secure
```{r}
Listing_df_1$secure <- ifelse(str_detect((Listing_df_1$amenities),"Safe|Security system|Lock")==TRUE,1,0)
table(Listing_df_1$secure)
select_var <- c(select_var, "secure")
```

#### 71 self_check_in / No need to use
```{r}
Listing_df_1$self_check_in <- ifelse(str_detect((Listing_df_1$amenities),"Self check-in")==TRUE,1,0)
table(Listing_df_1$self_check_in)
```

#### 72 smoking_allowed / No need to use
```{r}
Listing_df_1$smoking_allowed <- ifelse(str_detect((Listing_df_1$amenities),"Smoking allowed")==TRUE,1,0)
table(Listing_df_1$smoking_allowed)
```

#### 73 accessible / No need to use
```{r}
Listing_df_1$accessible <- ifelse(str_detect((Listing_df_1$amenities),"Step-free access|Wheelchair|Accessible")==TRUE,1,0)
table(Listing_df_1$accessible)
```

#### 74 event_suitable / No need to use
```{r}
Listing_df_1$event_suitable <- ifelse(str_detect((Listing_df_1$amenities),"Suitable for events")==TRUE,1,0)
table(Listing_df_1$event_suitable)
```

```{r}
Listing_df_2 <- Listing_df_1[,colnames(Listing_df_1) %in% select_var]
dim(Listing_df_1)
colnames(Listing_df_2)
```

```{r}
write.csv(Listing_df_2,"Airbnb_DataCleaning3.csv")
```

