---
title: "Visualization"
author: "Nam Tran"
date: "3/25/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(readr); library(tidyverse); library(dplyr); library(psych); library(PerformanceAnalytics); library(skimr); library(lessR); library(ggplot2); library(gridExtra); library(fastDummies); library(forecast); library(BMA); library(stats); library(olsrr); library(MASS); library(kableExtra); library(car); library(broom); library(glmulti); library(ggmap); library(rstudioapi); library(revgeo); library(RCurl);library(stringr); library(gsubfn)
```

```{r}
Listing_df <- read.csv("Airbnb_DataCleaning2.csv.csv")
Hosts_inf <- read.csv("Hosts_information.csv")
```

# Exploratory Data analysis
## Hosts Information

```{r}
#str(Hosts_inf)
```

### How many super host?
```{r}
table(Hosts_inf$host_is_superhost)
count(Hosts_inf[Hosts_inf$host_is_superhost =="t",])/nrow(Hosts_inf)*100
```
Superhosts takes 30% of hosts in LA

### How many host completed verification?
```{r}
table(Hosts_inf$host_identity_verified)
count(Hosts_inf[Hosts_inf$host_identity_verified =="t",])/nrow(Hosts_inf)*100
```
More than 78.8% host completed verification in Airbnb

## Listing Dataset
```{r}
#str(Listing_df)
```
Numerical variable: 

 * "host_response_rate"
 * "host_acceptance_rate"
 * "host_total_listings_count"
 * "price"
 * "number_of_reviews"
 * "number_of_reviews_ltm"
 * "number_of_reviews_l30d"
 * "review_scores_rating"
 * "review_scores_accuracy"
 * "review_scores_cleanliness"
 * "review_scores_checkin"
 * "review_scores_communication"
 * "review_scores_location"
 * "review_scores_value"
 * "reviews_per_month"
 
 Categorical Variables: 
 
 * "host_response_time"
 * "host_is_superhost"
 * "host_has_profile_pic"
 * "host_identity_verified"
 * "neighbourhood_cleansed"
 * "neighbourhood_group_cleansed"
 * "property_type"
 * "room_type"
 * "accommodates"
 * "bathrooms_text"
 * "bedrooms"
 * "beds"
 * "amenities"
 * "instant_bookable"
 * "Zip"
 * "City"
 
### Numerical Variables statistic Summary
```{r}
num_variales <- c("host_response_rate", "host_acceptance_rate", "host_total_listings_count", "price", "number_of_reviews", "number_of_reviews_ltm", "number_of_reviews_l30d", "review_scores_rating", "review_scores_accuracy", "review_scores_cleanliness", "review_scores_checkin", "review_scores_communication", "review_scores_location",  "review_scores_value", "reviews_per_month")
Num_sum_stat <- skimr::skim(Listing_df[,num_variales])
Num_sum_stat
```
 
### host_response_rate
```{r}
Listing_df$host_response_rate[is.na(Listing_df$host_response_rate)== TRUE] = mean(Listing_df$host_response_rate, na.rm = TRUE)
par(mfrow = c(1,2))
boxplot(Listing_df$host_response_rate ~ Listing_df$host_is_superhost, xlab = "Host is SuperHost or not", ylab = "Host Response Rate")
hist(Listing_df$host_response_rate, xlab = "Host Response Rate", main = "Distribution of Host Response Rate")

```

### host_acceptance_rate
```{r}
par(mfrow = c(1,2))
boxplot(Listing_df$host_acceptance_rate ~ Listing_df$host_is_superhost, xlab = "Host is SuperHost or not", ylab = "Host Acceptance Rate")
hist(Listing_df$host_acceptance_rate, xlab = "Host Acceptance Rate", main = "Distribution of Host Acceptance Rate")
Listing_df$host_acceptance_rate[is.na(Listing_df$host_acceptance_rate)== TRUE] = mean(Listing_df$host_acceptance_rate, na.rm = TRUE)
```
The Acceptance Rate of host is quite high, and there range of acceptance rate for SuperHost is significantly narrower than that for Non-SuperHost.
Based on the distribution, We will replace missing value for acceptance rate by the average of this variable.

### host_total_listings_count
```{r}
Hosts_Total_Listing <- as.data.frame(table(Listing_df$host_id))
colnames(Hosts_Total_Listing) <- c("host_id","total_listing")
Listing_df <- merge(Listing_df, Hosts_Total_Listing, by = "host_id")
```
```{r}
Listing_df$host_total_listings_count <- Listing_df$total_listing
Listing_df <- Listing_df[,-c(48)]
```
```{r}
# Using Host information to examine total listings variable
par(mfrow = c(1,2))
boxplot(Hosts_inf$total_listing ~ Hosts_inf$host_is_superhost, xlab = "Host is SuperHost or not", ylab = "Total Listing", log ='y')
hist(Hosts_inf$total_listing, xlab = "Total Listing", main = "Distribution of Total Listing")
count(Hosts_inf[Hosts_inf$host_is_superhost == "t" & Hosts_inf$total_listing > 1,])/count(Hosts_inf[Hosts_inf$host_is_superhost == "t",])
count(Hosts_inf[Hosts_inf$host_is_superhost == "f" & Hosts_inf$total_listing > 1,])/count(Hosts_inf[Hosts_inf$host_is_superhost == "f",])
```
Most of hosts just own only 1 listing, however there are some hosts own more than 1 listing. The distribution range of total listing for SuperHost is wider than that of N0n-SuperHost, nearly 30% of SuperHost own at least 2 listings, while there are 22% Non-SupperHost owing at least 2 listings.

### price
```{r}

par(mfrow = c(1,2))
# boxplot(Listing_df[Listing_df$price < 3000,"price"] ~ Listing_df[Listing_df$price < 3000,"host_is_superhost"], xlab = "Host is SuperHost or not", ylab = "Price", log = "y")
boxplot(Listing_df$price  ~ Listing_df$host_is_superhost, xlab = "Host is SuperHost or not", ylab = "Price", log ="y")
hist(Listing_df$price, xlab = "Price", main = "Distribution of Price")
```

### number_of_reviews
```{r}
par(mfrow = c(1,2))
boxplot(Listing_df$number_of_reviews ~ Listing_df$host_is_superhost, xlab = "Host is SuperHost or not", ylab = "Number of Review")
hist(Listing_df$number_of_reviews, xlab = "Number of Review", main = "Distribution of Number of Review")
mean(Listing_df$number_of_reviews[Listing_df$host_is_superhost == 't'])
mean(Listing_df$number_of_reviews[Listing_df$host_is_superhost == 'f'])
```
Most of listings received less than 200 reviews. From the box plot, Listings of SuperHost received more reviews than Non-SuperHost do. Listings of SuperHost have 75 reviews on average, while Listings of Non-SuperHost have 30 reviews on average.

### number_of_reviews_ltm (the number of review the listings had in 12 months)
```{r}
par(mfrow = c(1,2))
boxplot(Listing_df$number_of_reviews_ltm[Listing_df$number_of_reviews_ltm<200] ~ Listing_df$host_is_superhost[Listing_df$number_of_reviews_ltm<200] , 
        xlab = "Host is SuperHost or not", ylab = "Number of Review in last 12 months")
hist(Listing_df$number_of_reviews_ltm, xlab = "Number of Review in last year", main = "Distribution of Number of Review")
mean(Listing_df$number_of_reviews_ltm[Listing_df$host_is_superhost == 't'])
mean(Listing_df$number_of_reviews_ltm[Listing_df$host_is_superhost == 'f'])
```
Similarly, we could see that listings of Non-SuperHost have fewer reviews than SuperHosts. Listing of Non-superHost have 6 reviews on average inlast 12 months, while that of SuperHost is 17 reviews.

### review_scores_rating
```{r}
par(mfrow = c(1,2))
boxplot(Listing_df$review_scores_rating ~ Listing_df$host_is_superhost, xlab = "Host is SuperHost or not", ylab = "Review Score Rate")
hist(Listing_df$review_scores_rating, xlab = "Review Score", main = "Distribution of Review Score")
mean(Listing_df$review_scores_rating[Listing_df$host_is_superhost == 't'])
mean(Listing_df$review_scores_rating[Listing_df$host_is_superhost == 'f'])
```
Listings of SuperHost have higher review Score, around 4.88, while that of Non-SuperHost is 4.6

### review_scores_accuracy
```{r}
par(mfrow = c(1,2))
boxplot(Listing_df$review_scores_accuracy ~ Listing_df$host_is_superhost, xlab = "Host is SuperHost or not", ylab = "Score of Accuracy")
hist(Listing_df$review_scores_accuracy, xlab = "Score of Accuracy", main = "Distribution of Score Accuracy")
mean(Listing_df$review_scores_accuracy[Listing_df$host_is_superhost == 't'])
mean(Listing_df$review_scores_accuracy[Listing_df$host_is_superhost == 'f'])
```
The averavege accuracy score of SuperHost is higher than that of Non-SuperHost

### review_scores_cleanliness
```{r}
par(mfrow = c(1,2))
boxplot(Listing_df$review_scores_cleanliness ~ Listing_df$host_is_superhost, xlab = "Host is SuperHost or not", ylab = "Score of Cleanliess")
hist(Listing_df$review_scores_cleanliness, xlab = "Score of Cleanliness", main = "Distribution of Score Cleanliness")
mean(Listing_df$review_scores_cleanliness[Listing_df$host_is_superhost == 't'])
mean(Listing_df$review_scores_cleanliness[Listing_df$host_is_superhost == 'f'])
```
Similarly, we could see that usually the scores of cleanliness of SuperHost are higher than that of Non-SuperHost

### review_scores_checkin
```{r}
par(mfrow = c(1,2))
boxplot(Listing_df$review_scores_checkin ~ Listing_df$host_is_superhost, xlab = "Host is SuperHost or not", ylab = "Score of Check In")
hist(Listing_df$review_scores_checkin, xlab = "Score of Cleanliness", main = "Distribution of Score Check In")
mean(Listing_df$review_scores_checkin[Listing_df$host_is_superhost == 't'])
mean(Listing_df$review_scores_checkin[Listing_df$host_is_superhost == 'f'])
```

### review_scores_communication
```{r}
par(mfrow = c(1,2))
boxplot(Listing_df$review_scores_communication ~ Listing_df$host_is_superhost, xlab = "Host is SuperHost or not", ylab = "Score of Communication")
hist(Listing_df$review_scores_communication, xlab = "Score of Communication", main = "Distribution of Score Communication")
mean(Listing_df$review_scores_communication[Listing_df$host_is_superhost == 't'])
mean(Listing_df$review_scores_communication[Listing_df$host_is_superhost == 'f'])
```

### review_scores_location
```{r}
par(mfrow = c(1,2))
boxplot(Listing_df$review_scores_location ~ Listing_df$host_is_superhost, xlab = "Host is SuperHost or not", ylab = "Score of Location")
hist(Listing_df$review_scores_location, xlab = "Score of Location", main = "Distribution of Score Location")
mean(Listing_df$review_scores_location[Listing_df$host_is_superhost == 't'])
mean(Listing_df$review_scores_location[Listing_df$host_is_superhost == 'f'])
```

### review_scores_value
```{r}
par(mfrow = c(1,2))
boxplot(Listing_df$review_scores_value ~ Listing_df$host_is_superhost, xlab = "Host is SuperHost or not", ylab = "Score of Value")
hist(Listing_df$review_scores_value, xlab = "Score of Value", main = "Distribution of Score Value")
mean(Listing_df$review_scores_value[Listing_df$host_is_superhost == 't'])
mean(Listing_df$review_scores_value[Listing_df$host_is_superhost == 'f'])
```
Overall, listings of SuperHost has higher review score of Non-superHost in every aspects (accuracy, cleanliness, checkin, communication, location, value)

### reviews_per_month
```{r}
par(mfrow = c(1,2))
boxplot(Listing_df$reviews_per_month ~ Listing_df$host_is_superhost, xlab = "Host is SuperHost or not", ylab = "Review per month", log ="y")
hist(Listing_df$reviews_per_month, xlab = "Reviews per month", main = "Review per Month")
mean(Listing_df$reviews_per_month[Listing_df$host_is_superhost == 't'])
mean(Listing_df$reviews_per_month[Listing_df$host_is_superhost == 'f'])
```
### Correllation Matrix
```{r}
num_variales2 <- c("host_response_rate", "host_acceptance_rate", "host_total_listings_count", "price", "number_of_reviews", "number_of_reviews_ltm", "review_scores_rating", "review_scores_accuracy", "review_scores_cleanliness", "review_scores_checkin", "review_scores_communication", "review_scores_location",  "review_scores_value", "reviews_per_month")
round(cor(Listing_df[,num_variales2]),3)
```
From the correllation Matrix, there a strong positive relation between review scores variables.

### Categorical Variables Exploratory
```{r}
Cat_Variables <- c("host_response_time", "host_is_superhost", "host_has_profile_pic", "host_identity_verified", "neighbourhood_cleansed", "neighbourhood_group_cleansed", "property_type", "room_type","accommodates", "bathrooms_text" , "bedrooms", "beds", "amenities", "instant_bookable", "Zip", "City")
```

### host_response_time
```{r}
# host_response_time has a strong relationship with host_response_rate, therefore we will not consider host_response_time in our models.

Response_time.Plot1 <- ggplot(Listing_df[Listing_df$host_response_time !="N/A",], aes(x = host_response_time, fill = host_is_superhost)) + 
  geom_bar(position = "dodge") + labs(y="Count of Response Time",title="SuperHost and Non-SuperHost by Response Rate")

Response_time.Plot2 <-ggplot(Listing_df[Listing_df$host_response_time !="N/A",], aes(x = host_response_time, y = length(host_is_superhost), fill = host_is_superhost)) + 
  geom_col(position = "fill")  
#Proportion between YES and NO
Response_time.Plot1 
Response_time.Plot2 
```
### host_has_profile_pic
```{r}
Listing_df$host_has_profile_pic[Listing_df$host_has_profile_pic == ""] = "t"
table(Listing_df$host_has_profile_pic)
```
```{r}
Profile_Pic_time.Plot1 <- ggplot(Listing_df, aes(x = host_has_profile_pic, fill = host_is_superhost)) + 
  geom_bar(position = "dodge") + labs(y="Count of Host has profile picture",title="SuperHost and Non-SuperHost by Profile picture")
Profile_Pic_time.Plot1
```
We could see that all SuperHosts show their profile picture, which build the trust to their customers. Most 



```{r}
# We don't consider the effects of number of review in last 30 days because 30 days is sort period and that is depended on the time that data is collected.
# host_response_time has a strong relationship with host_response_rate, therefore we will not consider host_response_time in our models.
# host_has_profile_pic will be not considered in the model.
```


